A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-28 writeup/paper.tex
updated code for extracting data and compiling qc scores
new figures and tables

%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
\begin{figure}[h]
\centering
\includegraphics[height=\linewidth,angle=270]{figures/completiontime}
\caption{Time (in days) to complete all HITs in each language. Red bars show time until first HIT was started,
% relative to the time the first HIT in each language was started, relative to the time the first HIT in any language was started (first HIT started across all languages was Urdu). 
 blue bars show time until all HITs in each language were completed.}
\label{completion-time}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/quality-hitlang-new}
\caption{Translation quality of by source language}
\label{hitlangqual-bar}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Measured in this way, the average quality score across all HITs was just under \textbf{XXXX}. In general, countries which produced more translations did not produce lower quality translations, with India, Macedonia, and the US falling very close to average quality (figure \ref{quality-scatter}). In fact, likely as a result of the large number of India-based Turkers, most of the Indian languages fall above average quality, including Hindi, Telugu, Malayalam, Marathis, Tamil, Gujarati, Kannada, Bengali, and Punjabi, shown in figure \ref{hitlangqual-bar}. The notable exception is Urdu, which produced below average translations, likely due to the relatively low number of unique translators, making quality more susceptible to individual careless workers (see figure \ref{ass-scatter}).

%%%%%%%%%%%%%%% NATIVE LANGUAGE QUALITY BAR %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/quality-natlang-sorted}
\caption{Translation quality of native and non-native speakers}
\label{natlangqual-bar}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/quality-scatter-avgturkers-country-labeled-new}
\caption{Quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country.}
\label{quality-scatter}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
\begin{figure}[h]
\centering
%\includegraphics[height=\linewidth,angle=270]{figures/completiontime}
\includegraphics[width=\linewidth]{figures/completiontime.pdf}
\caption{Time (in days) to complete all HITs in each language. Red bars show time until first HIT was started,
% relative to the time the first HIT in each language was started, relative to the time the first HIT in any language was started (first HIT started across all languages was Urdu). 
 blue bars show time until all HITs in each language were completed.}
\label{completion-time-series}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/quality-hitlang-turkers}
\caption{Average estimated translation quality of by source language. Quality is calculated as the average number of control words which were correct translations of the source word, where "correct" means that the provided translation was judged to be synonymous with the known translation by workers in a second-pass HIT. Error bars show 95\% confidence intervals of the mean quality score across all translators for the language. Quality estimates are only show for languages with at least 50 active turkers. }
\label{hitlangqual-bar}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Measured in this way, the average quality score across all HITs was just under 0.5. In general, countries which produced more translations did not produce lower quality translations, with India, Macedonia, and the US falling very close to average quality (figure \ref{quality-scatter}). In fact, likely as a result of the large number of India-based Turkers, most of the Indian languages fall above average quality, including Hindi, Telugu, Malayalam, Marathis, Tamil, Gujarati, Kannada, Bengali, and Punjabi, shown in figure \ref{hitlangqual-bar}. The notable exception is Urdu, which produced below average translations, likely due to the relatively low number of unique translators, making quality more susceptible to individual careless workers (see figure \ref{ass-scatter}).

%%%%%%%%%%%%%%% NATIVE LANGUAGE QUALITY BAR %%%%%%%%%%%
%\begin{figure*}[h]
%\centering
%\includegraphics[width=6in]{figures/quality-natlang-sorted}
%\caption{Translation quality of native and non-native speakers}
%\label{natlangqual-bar}
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=6in]{figures/quality-scatter-avgturkers-country-labeled-turkers}
\caption{Estimated quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country. Quality is calculated as the average number of control words which were correct translations of the source word, where "correct" means that the provided translation was judged to be synonymous with the known translation by workers in a second-pass HIT. Figure represents data from approx. 281,000 assignments for which geolocation was known.}
\label{quality-scatter}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
